---
title: "Individual2"
author: "Ibrahim Murat Oztok"
date: "2/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 
```

##1
```{r}
summary(choco$Rating)
boxplot(choco$Rating) 
hist(choco$Rating)
```
<br>
<br>
<br>
Our ratings are left skewed(negatively skewed) , there are few outliers.
We can see from our summary statistics that our range is between 1.00 to 4.00


##2
We can see some locations have higher ratings than the others. We can also see the companies that
are located in Chile has the highest average rating and companies that are located in India and PR have the
lowest average ratings
```{r}
library(dplyr)
LocationRatings <- choco %>% group_by(Location) %>% summarise(avgRating = mean(Rating))
print(LocationRatings)
```

Let's look at the highest 10 company locations that have their average rating higher than the others.
```{r}
best10 <- head(LocationRatings[order(LocationRatings$avgRating,decreasing = T),], 10)
print(best10)
barplot(best10$avgRating, names.arg = best10$Location, xlab="Location",ylab="Ratings",col="blue",border="red")
```

## Analysis
I chose to look at if there is any connection between the number of ingredients and chocacalte ratings.
Let's remember that Ingredients column ("#" = represents the number of ingredients in the chocolate; B = Beans, S = Sugar, S* = Sweetener other than white cane or beet sugar, C = Cocoa Butter, V = Vanilla, L = Lecithin, Sa = Salt)
```{r}
IngredientsRatings <- choco %>% group_by(Ingredients) %>% summarise(avgRating1 = mean(Rating))
print(IngredientsRatings)
best22 <- head(IngredientsRatings[order(IngredientsRatings$avgRating1,decreasing = T),], 22)
print(best22) 
barplot(best22$avgRating1, names.arg = best22$Ingredients, xlab="Ingredients",ylab="Ratings",col="red",border="blue")
```
<br>
<br>
We can see that there is no direct correlation between number of ingredients and chocolate ratings. What effects the rating is what goes into the chocolate.
Our highest rated ingredients combination is : B,S,C meaning Beans, Sugar, Cocoa Butter
Our lowest rated ingredients combination is :  B,S*,Sa  meaning Beans, Sweetener and S
